Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-06 proposalPres.tex
Update ProposalPres.tex
I added some slides to our presentation to reflect the different sections of our proposal document.

@@

% \begin{frame}{Literature Review}
%   \begin{block}{Multipath Interference}
%     \begin{itemize}
%       \item Proposed solutions to multipath interference
%       \begin{itemize}
%         \item Course estimation calculations such as recieved signal strength indicator (RSSI) and time difference of arrival (TDoA)
%         \item IEEE 802.11b wireless Ethernet device to measure RF signals
%         \item Sampling radio signal strength (RSS) at discrete points without too much deviation from the robot's desired position
%       \end{itemize}
%     \end{itemize}
%   \end{block}
%       \begin{figure}[b]
%         \centering
%         \includegraphics[width=0.40\textwidth]{figs/img/MultipathFading}
%         \caption{Multipath Fading}
%         %\label{fig:sysBlockDiag}
%     \end{figure}
% \end{frame}

@@

%----------------------------------
\begin{frame}{Other Considerations}
  \begin{block}{Factors}
  	\begin{small}
      \begin{itemize}
        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
and driving fatalities and injuries. As a result, people will be able to live longer and
healthier lives. By creating accurate models, we will help advance the development of
autonomous vehicles and make this a reality.
		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle. We will address this by creating a rigorous test plan for our models.
		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
		\item Global Factors: 
		\item Cultural Factors: 
		\item Social Factors: 
		\item Environmental Factors: 
		\item Business Factors: 
		\item Economic Factors: 
      \end{itemize}
     \end{small}
  \end{block}
\end{frame}

>>>>

\section{System Identification}

\begin{frame}{System Identification}
  \begin{block}{System Identification}
 \begin{itemize}
        \item System identification is the process of developing mathematical models for a dynamic system using the measurement of input and output signals of that system. The goal of the system identification methodology is to get an accurate estimation of the system response to any given input. Mathworks' MATLAB has the system identification toolbox, where a few existing examples demonstrate the working principle of this toolbox.
	\item 
	\item 
\end{itemize}
  \end{block}
\end{frame}

@@

@@

%--------------------------------

\section{System Architecture}

\begin{frame}{System Architecture}
  \begin{block}{}
 \begin{itemize}
        \item 
	\item 
	\item 
\end{itemize}
  \end{block}
\end{frame}

\section{Preliminary Work}

\begin{frame}{Preliminary Work}
  \begin{block}{Preliminary Work}
 \begin{itemize}
        \item Documentation on MATLAB's System Identification Toolbox and tutorials
        \item Literature Review 
        \item Data Collection for steering, braking and acceleration subsystems
\end{itemize}
  \end{block}
  \begin {block}{Modeling}
  \begin{itemize}
  	\item All modeling of vehicle subsystems will be done using MATLAB's System Identification Toolbox feature. The subsystems can be grouped into four different categories: Single-Input-Single-Output, Multiple-Input-Multiple-Output, Single-Input-Multiple-Output, and Multiple-Input-Single-Output. 
  	\end{itemize}
  	\end{block}
\end{frame}

%----------------------------------
\section{Simulation Results}

\begin{frame}{Simulation Results}
  \begin{block}{}
 \begin{itemize}
        \item 
	\item 
	\item 
\end{itemize}
  \end{block}
\end{frame}

%----------------------------------
\section{Parts List}

\begin{frame}{Parts List}
  \begin{block}{Software and Hardware}
 \begin{itemize}
        \item Software
        \begin{itemize}
        \small
        \item MATLAB's System Identification Toolbox
        \item Vector CANAlyzer
        \end{itemize}
	\item Hardware
	\begin{itemize}
	\small
	\item Laptop
	\item PAC Mod
	\item CAN Case 
	\item CAN Bus
	\end{itemize}
\end{itemize}
  \end{block}
\end{frame}

%----------------------------------
\section{Timeline and Milestones}

\begin{frame}{Timeline and Milestones}
  \begin{block}{Milestones}
 \begin{itemize}
        \item Model steering subsystem 
	\item Test subsystem models with HIL system 
	\item Final report and presentation 
\end{itemize}
  \end{block}
\end{frame}

%----------------------------------
\section{Timeline and Milestones}

\begin{frame}{Timeline and Milestones}

\begin{frame}{Other Considerations}
  \begin{block}{Factors}
  	\begin{small}
      \begin{itemize}
        \item Public Health: Autonomous vehicles can make roads safer, which can prevent accidents
and driving fatalities and injuries. As a result, people will be able to live longer and
healthier lives. By creating accurate models, we will help advance the development of
autonomous vehicles and make this a reality.
		\item Public Safety: This is a relevant concern, because the real world implementations of inaccurate models could be disastrous since it is a self-driving vehicle. We will address this by creating a rigorous test plan for our models.
		\item Public Welfare: This factor is somewhat related to public safety and health in that we need to make sure that these vehicles are safe for people to use. How we will help
ensure this in our project is the same as how we will ensure public safety, by making sure we throughly test our models.
		\item Global Factors: 
		\item Cultural Factors: 
		\item Social Factors: 
		\item Environmental Factors: 
		\item Business Factors: 
		\item Economic Factors: 
      \end{itemize}
     \end{small}
  \end{block}
\end{frame}
